---
title: "simpleRegress"
author: "Chi Nguyen"
date: "summer2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Chest Chart

```{r}
simp <- lm(WEIGHT~CHEST,data=bears)
plot(WEIGHT~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

LENGTH CHART
```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)
abline(simp)
summary.lm(simp)
```

HEADLEN CHART
```{r}
simp <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

HEADWTH CHART
```{r}
simp <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

AGE CHART
```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

CHEST :
 Adjusted R-squared:  0.9262 RSE :33.08

NECK 
Adjusted R-squared:  0.87  RSE :43.91

LENGTH
Adjusted R-squared:  0.7423   RSE :61.83

HEADLEN
Adjusted R-squared:  0.69   RSE :67.81 

HEADWTH
Adjusted R-squared:  0.6064   RSE :76.41

AGE
Adjusted R-squared:  0.5526   RSE :81.47




