---
title: "simpleRegress"
author: "Chi Nguyen"
date: "summer2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ AGE  this is an example  

```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ HEADLEN  this is an example  
```{r}
simp <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ HEADWTH  this is an example  
```{r}
simp <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ LENGTH  this is an example  

```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ CHEST  this is an example  

```{r}
simp <- lm(WEIGHT~CHEST,data=bears)
plot(WEIGHT~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```




## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

Sumary of all the plot

For Neck- the rse for this graph was 43.91 while the Adjusted R-squared:   0.87 

For AGE- the rse for this graph was 81.47 while the Adjusted R-squared:   0.5526 

For HEADLEN- the rse for this graph was 67.81 while the Adjusted R-squared:   0.69 

For HEADWTH- the rse for this graph was 76.41 while the Adjusted R-squared: 0.6064   

For LENGTH- the rse for this graph was 61.83 while the Adjusted R-squared: 0.7423   

For CHEST -the rse for this graph was 33.08 while the Adjusted R-squared :0.9262

After looking at all the result of the graph we can see that the graph with the tightest grouping is the chest as its adjusted R-squared was 0.9262 which is the closest to 1 that we have. As well as the graph with the widest spread was age as its Adjusted R-squared was 0.5526 

